Thermodynamic fragments in magic state theories

### 2020-12-17 magic_paper.tex
Replied to comments

Moreover, for the problem of distilling pure magic states where $\epsilon'=0$ we obtain a upper bound on the unital fragment distillation rate $R=n'/n$ given by
\begin{equation}
R \leq \frac{\ln 3}{\ln (3-4 \epsilon)},
\end{equation}
which holds for all finite $n$. 
In comparison, the bound from mana gives 
\begin{equation}
	R_{\rm{mana}} \leq \frac{\ln \frac{5}{3}}{\ln \left(\frac{5}{3} - \frac{8}{9}\epsilon \right)},
\end{equation}
a threshold which is looser than the one provided by majorization for all $\epsilon > 0$. For example, for $\epsilon = 0.4$ we obtain $R\le 3.27 $ while the mana bound gives $R_{\rm{mana}} \le 1.89$. \ddd{[Am I making some mistake here?? Mana does better according to these numbers? Does it only do better for a region of $\epsilon$ values? Perhaps plot the functions together.]}

@@

Thermal operations coincide with fragment $\O_{\gamma_\beta}$ \nick{expand}. \ddd{[Completely vital. What Hamiltonian are you choosing? Note you can choose it to make life easy for yourself. E.g. $H=Z$ for example.]}
The Wigner distribution of any thermal state $\gamma_\beta$ always consists of strictly positive components,
\begin{equation}
	\W[\bmx]{\gamma_\beta} = \frac{e^{-\beta \epsilon_{x_0}}}{d\Z_\beta}\ \text{for all}\ \bmx \in \pd,
\end{equation}
so pre-order $\prec_{\gamma_\beta}$ is well defined. \ddd{[Not clear where this equation comes from.]}

@@

However, higher copies are not sorted, for example
\begin{equation}
	\begin{split}
	\W{\gamma_\beta\too{2}} = \frac{1}{9\Z_\beta^2} \Bigg( &\overbrace{\overbrace{e^{-\beta 2E_0}}^3, \overbrace{e^{-\beta (E_0 + E_1)}}^3, \overbrace{e^{-\beta (E_0 + E_2)}}^3}^3, \\
	 &\overbrace{\overbrace{e^{-\beta (E_1 + E_0)}}^3, \overbrace{e^{-\beta 2E_1}}^3, \overbrace{e^{-\beta (E_1 + E_2)}}^3}^3, \\
	 &\overbrace{\overbrace{e^{-\beta (E_2 + E_0)}}^3, \overbrace{e^{-\beta (E_2 + E_1)}}^3, \overbrace{e^{-\beta 2E_2}}^3}^3 \Bigg).
	\end{split}
\end{equation}
\ddd{[Definitely impressed by this Latexing...but perhaps just give the multiplicities and spectrum values. I.e. ``(blah) with multiplicity (blah) and ...'']} For the Strange state we have
\begin{equation}
	\begin{split}
	\W{\noisys(\epsilon)\too{2}} = \Bigg( &\overbrace{\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^2}^1, \overbrace{ \left( -\frac{1}{3} + \frac{4}{9}\epsilon \right) \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)}^{8}, \\
	&\overbrace{\overbrace{ \left( -\frac{1}{3} + \frac{4}{9}\epsilon \right) \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)}^1, \overbrace{\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^2}^8}^8,  \Bigg).
	\end{split}
\end{equation}
\nick{We need to sort the distributions $\W{\gamma_\beta\too{2}}, \W{\noisys(\epsilon)\too{2}}$, so that the vector
\begin{equation}
	\tilde{\bm{w}} \coloneqq \left(\frac{(\W{\noisys(\epsilon)\too{2}})_1}{(\W{\sigma})_1}, \dots, \frac{(\W{\rho})_{81}}{(\W{\sigma})_{81}} \right)^T,
\end{equation}
is in decreasing order, i.e. $\tilde{\bm{w}} = \tilde{\bm{w}}^\downarrow$.
Then, we need to generalise for any number of copies $n$}

>>>>

Moreover, for the problem of distilling pure magic states where $\epsilon'=0$ we obtain a upper bound on the unital fragment distillation rate $R=n'/n$ given by
\begin{equation}
R \leq \frac{\ln (3-4 \epsilon)}{\ln 3},
\end{equation}
which holds for all finite $n$. 
In comparison, the bound from mana gives 
\begin{equation}
	R_{\rm{mana}} \leq \frac{\ln \left(\frac{5}{3} - \frac{8}{9}\epsilon \right)}{\ln \frac{5}{3}},
\end{equation}
a threshold which is looser than the one provided by majorization for all $\epsilon > 0$ as illustrated in~\cref{fig:distill_bounds}.
For example, for $\epsilon = 0.4$ we obtain $R\le 0.31 $ while the mana bound gives $R_{\rm{mana}} \le 0.53$.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/distill_bounds.pdf}
    \caption{\textbf{Distillation rate in unital fragment.} Distillation rates obtained by mana and majorization are plotted for $\epsilon' = 0$, up to noise levels $\epsilon_{\rm{max}} = \frac{3}{7}$.
    Majorization consistently provides stricter rates as proven in~\cref{thm:bounds}.
    }
    \label{fig:distill_bounds}
\end{figure}

@@

Thermal operations coincide with fragment $\O_{\gamma_\beta}$ \nick{expand}. \ddd{[Completely vital. What Hamiltonian are you choosing? Note you can choose it to make life easy for yourself. E.g. $H=Z$ for example.]}\nick{$X, Z$ are not Hermitian. Currently a general Hamiltonian with spectrum $(\epsilon_0,\epsilon_1,\epsilon_2)$.}
The Wigner distribution of any thermal state $\gamma_\beta$ is calculated directly by the definition in~\cref{eq:wstate},
\begin{equation}
	\W[\bmx]{\gamma_\beta} = \frac{e^{-\beta \epsilon_{x_0}}}{d\Z_\beta}\ \text{for all}\ \bmx \in \pd,
\end{equation}
and always consists of strictly positive components, so pre-order $\prec_{\gamma_\beta}$ is well defined.

@@

However, higher copies are not sorted, for example
\begin{equation}
	\begin{split}
	\W{\gamma_\beta\too{2}} = \frac{1}{9\Z_\beta^2} \Bigg( &\overbrace{\overbrace{e^{-\beta 2E_0}}^3, \overbrace{e^{-\beta (E_0 + E_1)}}^3, \overbrace{e^{-\beta (E_0 + E_2)}}^3}^3, \\
	 &\overbrace{\overbrace{e^{-\beta (E_1 + E_0)}}^3, \overbrace{e^{-\beta 2E_1}}^3, \overbrace{e^{-\beta (E_1 + E_2)}}^3}^3, \\
	 &\overbrace{\overbrace{e^{-\beta (E_2 + E_0)}}^3, \overbrace{e^{-\beta (E_2 + E_1)}}^3, \overbrace{e^{-\beta 2E_2}}^3}^3 \Bigg).
	\end{split}
\end{equation}
\ddd{[Definitely impressed by this Latexing...but perhaps just give the multiplicities and spectrum values. I.e. ``(blah) with multiplicity (blah) and ...'']} \nick{So the problem is that the exact position of each component matters, e.g. thermal state component $e^{-\beta 2E_0}$ corresponds to a positive Strange state component in one position and a negative Strange state component in another.} 
For the Strange state we have
\begin{equation}
	\begin{split}
	\W{\noisys(\epsilon)\too{2}} = \Bigg( &\overbrace{\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^2}^1, \overbrace{ \left( -\frac{1}{3} + \frac{4}{9}\epsilon \right) \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)}^{8}, \\
	&\overbrace{\overbrace{ \left( -\frac{1}{3} + \frac{4}{9}\epsilon \right) \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)}^1, \overbrace{\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^2}^8}^8,  \Bigg).
	\end{split}
\end{equation}
\nick{We need to sort the distributions $\W{\gamma_\beta\too{2}}, \W{\noisys(\epsilon)\too{2}}$, so that the vector
\begin{equation}
	\tilde{\bm{w}} \coloneqq \left(\frac{(\W{\noisys(\epsilon)\too{2}})_1}{(\W{\sigma})_1}, \dots, \frac{(\W{\rho})_{81}}{(\W{\sigma})_{81}} \right)^T,
\end{equation}
is in decreasing order, i.e. $\tilde{\bm{w}} = \tilde{\bm{w}}^\downarrow$.
Then, we need to generalise for any number of copies $n$}
